\textit{Monami} as an oscillatory hydrodynamic instability in a submerged sea grass bed

### 2014-11-05 Paper/grass.tex
changed intro one sentance

\maketitle
\words{80} Sea grasses exhibit a rich set of dynamical behavior due to their collective interaction with fluid flows.  
The hydrodynamic processes resulting from this behavior influence many environmental processes such as sediment, contaminant, and dissolved oxygen transport, plant growth, and biomass production  \cite{Fonseca87,Grizzle96,Nepf99,Nepf2012}. 
One such response of the submerged grass beds to steady currents is the formation of coherent large amplitude oscillations, known as \monami ~\cite{AckermanOkubo93}.  
In this letter, we provide a hydrodynamic mechanism for the onset of these coherent oscillations.

>>>>

\maketitle
\words{80} Sea grasses exhibit a rich set of dynamical behavior due to their collective interaction with fluid flows.  
The hydrodynamic processes resulting from this behavior influence many environmental processes such as sedimentation, transportation of dissolved oxygen, plant growth, and biomass production  \cite{Fonseca87,Grizzle96,Nepf99,Nepf2012}. 
One such response of the submerged grass beds to steady currents is the formation of coherent large amplitude oscillations, known as \monami ~\cite{AckermanOkubo93}.  
In this letter, we provide a hydrodynamic mechanism for the onset of these coherent oscillations.
